### 2018-07-05 paper/1-intro.tex
Changes to intro

\item We show that we can instantiate our abstractions to describe the essence
of a variety of different real-life build systems, including \Make, \Shake,
\Bazel, \CloudBuild, \Buck, \Nix, and \Excel, each in a dozen lines of code
or so (\S\ref{sec-implementations}). Doing this modelling in a single setting
allows the differences and similarities between these huge systems to be
brought out clearly.

@@

Papers about ``frameworks'' are often fuzzy.  This one is not: all our
abstractions are defined in Haskell, and we have (freely-available)
executable models of all the build systems we describe.

>>>>

\item We show that we can instantiate our abstractions to describe the essence
of a variety of different real-life build systems, including \Make, \Shake,
\Bazel, \CloudBuild, \Buck, \Nix, and \Excel\footnote{\Excel appears very
different to the others but, seen through the lens of this paper, it is very
close indeed.}, each by the composition of the two design choices
(\S\ref{sec-implementations}). Doing this modelling in a single setting
allows the differences and similarities between these huge systems to be
brought out clearly.

@@

% Papers about ``frameworks'' are often fuzzy.  This one is not: all our
% abstractions are defined in Haskell, and we have (freely-available)
% executable models of all the build systems we describe.
